Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and its audio-description

### 2020-07-20 paper/main.tex
results for individual brain slices & Bland-Altman-Plots

audio-only (AO) stimulus. Some of the original categories (female, females,
fname; male, males, mname; face, head; object, objects; see Table
\ref{tab:descr-nouns-rules}) were pooled into 11 new categories (sex\_f; sex\_m; fahead; object).

@@

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/regressor-corr} \caption{Pearson
        correlation coefficients of the regressors used in the analysis of the
        audio-description (blue; see Table \ref{tab:ao-events} for a
        description) and audio-visual movie (red; see Table
        \ref{tab:av-events}).
    \label{fig:reg-corr}
\end{figure*}

@@

\todo[inline]{contrasts are ordered by ``how well they make sense'' according to
theory, ``quality of auditory cue'', and amount of events/data. Hence, the were
assumed to result in more and more shitty results; at the moment all 8 contrasts
are used in the result (figure)}

% intro
For the AO stimulus, we created eight $t$-contrasts to isolate presumably
correlating with increased hemodynamic activity in the PPA by contrasting
different kind descriptive nouns. % furniture: blurred border between groom and
object Furniture was not included in one of the contrast because it can be
considered as an object or geometry-defining structure of a room.
% negative control contrasts
Five $t$-contrasts (see Table \ref{tab:ao-contrasts} we created for negative
control purposes to test if increased activation in the PPA was correlated with
moment of cuts and therefore correlated with a possible change in the
soundscape.

@@

\label{tab:ao-contrasts}
\footnotesize
\begin{tabular}{lll}
\toprule
\textbf{nr.} &  \textbf{contrast} & \textbf{purpose} \\
\midrule
1 & geo, groom > all non-geo & PPA \tabularnewline
2 & geo, groom, se\_new > all non-geo & PPA \tabularnewline
3 & gro
om, se\_new, se\_old > all non-geo & PPA \tabularnewline
4 & geo > all non-geo & PPA \tabularnewline
5 & groom > all non-geo & PPA \tabularnewline
6 & se\_new > all non-geo & PPA \tabularnewline
7 & se\_new, se\_old > all non-geo & PPA \tabularnewline
8 & se\_new > se\_old & PPA \tabularnewline
9 & vse\_new > vpe\_old & control at moments of cuts \tabularnewline
10 & vse\_new, vpe\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
11 & vse\_new > vse\_old & control at moments of cuts \tabularnewline
12 & vse\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
13 & vse\_new, vpe\_new > vpe\_old & control at moments of cuts \tabularnewline
\end{tabular}
\end{table*}

@@

% HOW TO WRITE METHODS SEXTION
% first paragraph (cause most readers don't read methods beforehand
% summarizes the overall approach to the problem outlined in the intro
% key innovative methods that were developed
% -> gist of the methods that were used

% subsequent paragraphs start with a sentence or two
% that set up the question that the paragraph answers
% e.g. ``To verify that there are no artifacts..''
% What is the test-retest reliability of our measure?''
% “We next tested whether Ca2+ flux through Ca2+ channels was involved.''
% Middle of the paragraph presents data and logic that pertain to the question,
% paragraph ends with a sentence that answers the question
% For example, it may conclude that none of potential artifacts were detected.
% Each paragraph convinces the reader of answer given in its last sentence.
% The result of each paragraph is a logical statement

\subsection{primary contrasts}
% AO
The primary $t$-contrast for the audio-description comparing geometry-related
nouns to non geometry-related nouns spoken by the audio-description's narrator
(\texttt{geo, groom > all non-geo} yielded six significant clusters (see Table
\ref{tab:res-ao-group1}, Figure \ref{fig:group-slices}).
% precuneus
Two homologous clusters in the ventral precuneus extending into the
retrosplenial cortex.
% PPA
Two homologous clusters in the lingual gyrus, occipital and temporal fusiform
gyrus, and posterior parahippocampal cortex \todo{the clusters are small but
that's what the Harvard-Oxford Atlas suggests, probably because at borders of
the areas}.
% LOC
And finally, two homologous clusters in the superior lateral occipital cortex.

% AV
The primary $t$-contrast for the movie comparing cuts to a new setting with cuts
to a familiar perspective (\texttt{vse\_new > vpe\_old}) yielded three
significant clusters (see Table \ref{tab:res-av-group1}, Figure
\ref{fig:group-slices}).
% LOC
Two clusters in the superior lateral occipital cortex (left bigger than right).
% PPA + others.
And one one cluster spanning across the midline and comprising intracalcarine
and cuneal cortex, lingual gyrus and retrosplenial cortex,  occipital fusiform
gyrus and temporal fusiform gyrus, and parahippocampal cortex bilaterally.

\begin{table*}[t]
    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected)
        of the primary $t$-contrast for the audio-description comparing
        geometry-related nouns to non geometry-related nouns spoken by the
        audio-description's narrator (\texttt{geo, groom > all non-geo}).
        Clusters sorted by voxel size.
    The first brain structure given contains the voxel with the maximum Z-Value,
followed by brain structures from posterior to anterior, and partially covered
areas (l. = left; r. = right; c. = cortex; g. = gyrus).}
    \label{tab:res-ao-group1}
\begin{tabular}{rrrrrrrrrp{3cm}}
\toprule
& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{4-6} \cmidrule{7-9}
voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
\midrule
188 & 5.96E-08 & 4.48 & -17.5 & -65.5 & 25.5 & -14.7 & -59.1 & 15.2 & l. precuneus \\
164 & 2.38E-07 & 4.47 & 17.5 & -58 & 23 & 15.6 & -55.6 & 16 & r. precuneus; \\
83 & 0.000128 & 4.48 & 27.5 & -43 & -17 & 27.2 & -41.1 & -14 & r. temporal (occipital) fusiform c.; posterior parahippocampal g. \\
73 & 0.000318 & 3.93 & -22.5 & -43 & -12 & -23.9 & -43.6 & -11.2 & l. lingual g.; temporal (occipital) fusiform g., posterior parahippocampal c. \\
63 & 0.000824 & 4.1 & 40 & -75.5 & 30.5 & 40.9 & -76.3 & 28.6 & r. superior lateral occipital c. \\
37 & 0.0129 & 4.24 & -37.5 & -78 & 33 & -38.4 & -79.5 & 28.9 & l. superior lateral occipital c. \\
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}[t]
    \caption{Significant clusters (Z-Threshold Z>3.4; p<.05 cluster-corrected)
        of the primary $t$-contrast for the movie comparing cuts to a new
        setting with cuts to a familiar perspective (\texttt{vse\_new >
        vpe\_old}).
Clusters sorted by voxel size.
The first brain structure given contains the voxel with the maximum Z-Value,
followed by brain structures from posterior to anterior, and partially covered
areas (l. = left; r. = right; c. = cortex; g. = gyrus).}
\label{tab:res-av-group1}
\begin{tabular}{rrrrrrrrrp{3cm}}
\toprule
& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{4-6} \cmidrule{7-9}
voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
\midrule
3003 & 0 & 5.31 & 22.5 & -45.5 & -12 & 4.53 & -63.3 & -3.72 & r. lingual g.; r
cuneal c., intracalcarine c., bilaterally occipital fusiform g., temporal fusiform c., posterior parahippocampal c.  \\
154 & 6.56E-07 & 4.46 & -35 & -83 & 28 & -32.8 & -86.2 & 21.4 & l. superior lateral occipital c. \\
121 & 7.69E-06 & 4.65 & 25 & -80.5 & 25.5 & 23.7 & -83.8 & 25.4 & r. superior lateral occipital cortex \\
\bottomrule
\end{tabular}
\end{table*}

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/group-slices}
    \caption{Mixed-effects group-level (N=14) GLM results. Significant clusters
        (Z>3.4, p<0.05 cluster-corrected) are overlaid on the MNI152 T1-weighted
        head template (grey).
        Light grey: The audio-description's field-of-view
        (cf. \citep{hanke2014audiomovie}).
        Blue: the primary $t$-contrast for the audio-description comparing
        geometry-related nouns to non geometry-related nouns spoken by the
        audio-description's narrator (\texttt{geo, groom > all non-geo}).
        Red: the primary $t$-contrast for the movie comparing cuts to a new
        setting with cuts to a familiar perspective (\texttt{vse\_new >
        vpe\_old)}.
        Black: outline of overlapping individual PPA ROIs.
        \citep{sengupta2016extension}.}
    \label{fig:group-slices}
\end{figure*}

\subsection{individual results}
See Figure \ref{fig:subs-thresh-ppa}; AO / AV to localizer ratios

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/subs-thresh-ppa}
    \caption{Fixed-effects individual-level GLM results (Z>3.4, p<0.05
        cluster-corrected). The brains of the 14 subjects are aligned via
        non-linear transformation to a study-specific T2* group template that is
    co-registered to the MNI152 template with an affine transformation (12
degrees of freedom) to facilitate comparisons across subjects.
        Light grey: The audio-description's field-of-view
        (cf. \citep{hanke2014audiomovie}).
        Blue: the primary $t$-contrast for the audio-description comparing
        geometry-related nouns to non geometry-related nouns spoken by the
        audio-description's narrator (\texttt{geo, groom > all non-geo}).
        Red: the primary $t$-contrast for the movie comparing cuts to a new
        setting with cuts to a familiar perspective (\texttt{vse\_new >
        vpe\_old)}.
        Black: outline of subject-specific PPA ROI.}

\label{fig:subs-thresh-ppa}
\end{figure*}

\subsection{Bland-Altman-Plots}
See Figure \ref{fig:bland-altman}

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/subjs_bland-altman.png}
    \caption{Bland-Altman-Plots for individual subjects}
    \label{fig:bland-altman}
\end{figure*}

@@

% AO
\todo{alle noch einmal im einzelnen angucken; was ist mit COPE 8, der ist in der
Abb. nicht drin; zeigt (noch) einer keine sign. cluster?}
% PPA
Six of seven AO contrasts show significant bilateral clusters in anterior
regions of the group PPA overlap (which is temporal occipital fusiform gyrus
regarding to co-registered Harvard-Oxford Cortical Structural Atlas).
% Precuneus = retrosplenial cortex ?
Six of seven contrasts show significant clusters in the ventral precuneus /
retrosplenial cortex (RSC).

% AV
% PPA
All five AV contrasts yielded significant bilateral clusters in (temporal)
occipital, fusiform cortex showing congruency with the group overlap of
individual PPA ROIs.
% Lingual Gyrus
Homologous clusters of three contrasts extend further into lingual gyrus.
% RSC
Three contrasts show significant bilateral clusters in RSC.
% LOC
Four contrasts show significant bilateral clusters in lateral occipital cortex

@@

>>>>

audio-only (AO) stimulus. Some of the annotation's original categories
    (female, females, fname; male, males, mname; face, head; object, objects;
    see Table\ref{tab:descr-nouns-rules})
    were pooled into 11 new categories (\texttt{sex\_f}; \texttt{sex\_m};
    \texttt{fahead}; \texttt{object}).

@@

\begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{figures/regressor-corr}
    \caption{Pearson
        correlation coefficients of the regressors used in the analysis of the
        audio-description (blue; see Table \ref{tab:ao-events} for a
        description) and audio-visual movie (red; see Table
        \ref{tab:av-events}).}
    \label{fig:reg-corr}
\end{figure*}

@@

\todo[inline]{contrasts are ordered by ``how well they make sense'' according to
theory, ``quality of auditory cue'', and amount of events/data. Hence, they were
assumed to result in more and more shitty results; at the moment all 8 contrasts
are used in the result (figure)}

% intro
For the AO stimulus, we created eight $t$-contrasts presumably correlating with
increased hemodynamic activity in the PPA by contrasting different kind
descriptive nouns.
% furniture: blurred border between groom and object
The categroy ``furniture'' (\texttt{furn} was not included in one of the
contrast because it can be considered as an object or geometry-defining
structure of a room.
% negative control contrasts
Five $t$-contrasts (see Table \ref{tab:ao-contrasts} we created for negative
control purposes to test if increased activation in the PPA was correlated with
moment of cuts and therefore correlated with a possible change in the
soundscape.

@@

\label{tab:ao-contrasts}
\footnotesize
\begin{tabular}{lll}
\toprule
\textbf{nr.} &  \textbf{contrast} & \textbf{purpose} \\
\midrule
1 & geo, groom > all non-geo & PPA \tabularnewline
2 & geo, groom, se\_new > all non-geo & PPA \tabularnewline
3 & groom, se\_new, se\_old > all non-geo & PPA \tabularnewline
4 & geo > all non-geo & PPA \tabularnewline
5 & groom > all non-geo & PPA \tabularnewline
6 & se\_new > all non-geo & PPA \tabularnewline
7 & se\_new, se\_old > all non-geo & PPA \tabularnewline
8 & se\_new > se\_old & PPA \tabularnewline
9 & vse\_new > vpe\_old & control at moments of cuts \tabularnewline
10 & vse\_new, vpe\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
11 & vse\_new > vse\_old & control at moments of cuts \tabularnewline
12 & vse\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
13 & vse\_new, vpe\_new > vpe\_old & control at moments of cuts \tabularnewline
\end{tabular}
\end{table*}

@@

\todo[inline]{at the moment I tend to reporting the stability of contrast first,
and then go on to report the primary contrasts for group and individuals; both
has pros and cons}

% HOW TO WRITE METHODS SEXTION
% first paragraph (cause most readers don't read methods beforehand
% summarizes the overall approach to the problem outlined in the intro
% key innovative methods that were developed
% -> gist of the methods that were used
The goal of this study was to exploratorily investigate how the PPA responds to
auditory cues embedded in a naturalistic audio-only stimulus. We further aimed
at comparing these results to results to an audio-visual naturalistic stimulus
and to results from a dedicated visual localizer experiment.

We did this by using GLM... blabla...
% subsequent paragraphs start with a sentence or two
% that set up the question that the paragraph answers
% e.g. ``To verify that there are no artifacts..''
% What is the test-retest reliability of our measure?''
% “We next tested whether Ca2+ flux through Ca2+ channels was involved.''
% Middle of the paragraph presents data and logic that pertain to the question,
% paragraph ends with a sentence that answers the question
% For example, it may conclude that none of potential artifacts were detected.
% Each paragraph convinces the reader of answer given in its last sentence.
% The result of each paragraph is a logical statement

@@

% AO
\todo{alle noch einmal im einzelnen angucken; was ist mit COPE 8, der ist in der
Abb. nicht drin; zeigt (noch) einer keine sign. cluster?}
% intro
We combined different event categories to create eight contrasts that provided
different congruency with the spatial layout hypothesis and different amount of
data/events.
% PPA
Six of seven AO contrasts show significant bilateral clusters in anterior
regions of the group PPA overlap (which is temporal occipital fusiform gyrus
regarding to co-registered Harvard-Oxford Cortical Structural Atlas).
% Precuneus = retrosplenial cortex ?
Six of seven contrasts show significant clusters in the ventral precuneus /
retrosplenial cortex (RSC).

% AV
% intro
We also created five contrasts for the audio-visual stimulus by using different
kind of cuts to be able to compare results across perceptual modalities.
% PPA
All five AV contrasts yielded significant bilateral clusters in (temporal)
occipital, fusiform cortex showing congruency with the group overlap of
individual PPA ROIs.
% Lingual Gyrus
Homologous clusters of three contrasts extend further into lingual gyrus.
% RSC
Three contrasts show significant bilateral clusters in RSC.
% LOC
Four contrasts show significant bilateral clusters in lateral occipital cortex

@@

\subsection{primary contrasts}
% intro
\todo{intro sentence regarding the primary contrasts}
% the contrast in detail
The primary $t$-contrast for the audio-description comparing geometry-related
nouns to non geometry-related nouns spoken by the audio-description's narrator
(\texttt{geo, groom > all non-geo} yielded six significant clusters (see Table
\ref{tab:res-ao-group1}, Figure \ref{fig:group-slices}).
% precuneus
Two homologous clusters in the ventral precuneus extending into the
retrosplenial cortex.
% PPA
Two homologous clusters in the lingual gyrus, occipital and temporal fusiform
gyrus, and posterior parahippocampal cortex \todo{the clusters are small but
that's what the Harvard-Oxford Atlas suggests, cluster is at borders of the
areas}.
% LOC
And finally, two homologous clusters in the superior lateral occipital cortex.

% AV
% intro
\todo{intro sentence regarding the primary contrasts}
% the contrast in detail
The primary $t$-contrast for the movie comparing cuts to a new setting with cuts
to a familiar perspective (\texttt{vse\_new > vpe\_old}) yielded three
significant clusters (see Table \ref{tab:res-av-group1}, Figure
\ref{fig:group-slices}).
% LOC
Two clusters in the superior lateral occipital cortex (left bigger than right).
% PPA + others.
And one one cluster spanning across the midline and comprising intracalcarine
and cuneal cortex, lingual gyrus and retrosplenial cortex,  occipital fusiform
gyrus and temporal fusiform gyrus, and parahippocampal cortex bilaterally.

\begin{table*}[t]
    \caption{Significant clusters (z-threshold Z>3.4; p<.05 cluster-corrected)
        of the primary $t$-contrast for the audio-description comparing
        geometry-related nouns to non geometry-related nouns spoken by the
        audio-description's narrator (\texttt{geo, groom > all non-geo}).
        Clusters sorted by voxel size.
    The first brain structure given contains the voxel with the maximum Z-Value,
followed by brain structures from posterior to anterior, and partially covered
areas (l. = left; r. = right; c. = cortex; g. = gyrus).}
    \label{tab:res-ao-group1}
\begin{tabular}{rrrrrrrrrp{3cm}}
\toprule
& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{4-6} \cmidrule{7-9}
voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
\midrule
188 & 5.96E-08 & 4.48 & -17.5 & -65.5 & 25.5 & -14.7 & -59.1 & 15.2 & l. precuneus \\
164 & 2.38E-07 & 4.47 & 17.5 & -58 & 23 & 15.6 & -55.6 & 16 & r. precuneus; \\
83 & 0.000128 & 4.48 & 27.5 & -43 & -17 & 27.2 & -41.1 & -14 & r. temporal (occipital) fusiform c.; posterior parahippocampal g. \\
73 & 0.000318 & 3.93 & -22.5 & -43 & -12 & -23.9 & -43.6 & -11.2 & l. lingual g.; temporal (occipital) fusiform g., posterior parahippocampal c. \\
63 & 0.000824 & 4.1 & 40 & -75.5 & 30.5 & 40.9 & -76.3 & 28.6 & r. superior lateral occipital c. \\
37 & 0.0129 & 4.24 & -37.5 & -78 & 33 & -38.4 & -79.5 & 28.9 & l. superior lateral occipital c. \\
\bottomrule
\end{tabular}
\end{table*}

\begin{table*}[t]
    \caption{Significant clusters (z-threshold Z>3.4; p<.05 cluster-corrected)
        of the primary $t$-contrast for the movie comparing cuts to a new
        setting with cuts to a familiar perspective (\texttt{vse\_new >
        vpe\_old}).
Clusters sorted by voxel size.
The first brain structure given contains the voxel with the maximum Z-Value,
followed by brain structures from posterior to anterior, and partially covered
areas (l. = left; r. = right; c. = cortex; g. = gyrus).}
\label{tab:res-av-group1}
\begin{tabular}{rrrrrrrrrp{3cm}}
\toprule
& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{4-6} \cmidrule{7-9}
voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
\midrule
3003 & 0 & 5.31 & 22.5 & -45.5 & -12 & 4.53 & -63.3 & -3.72 & r. lingual g.; r
cuneal c., intracalcarine c., bilaterally occipital fusiform g., temporal fusiform c., posterior parahippocampal c.  \\
154 & 6.56E-07 & 4.46 & -35 & -83 & 28 & -32.8 & -86.2 & 21.4 & l. superior lateral occipital c. \\
121 & 7.69E-06 & 4.65 & 25 & -80.5 & 25.5 & 23.7 & -83.8 & 25.4 & r. superior lateral occipital cortex \\
\bottomrule
\end{tabular}
\end{table*}

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/group-slices}
    \caption{Mixed-effects group-level (N=14) GLM results. Significant clusters
        (Z>3.4, p<.05 cluster-corrected) are overlaid on the MNI152 T1-weighted
        head template (grey).
        Light grey: The audio-description's field-of-view
        (cf. \citep{hanke2014audiomovie}).
        Blue: the primary $t$-contrast for the audio-description comparing
        geometry-related nouns to non geometry-related nouns spoken by the
        audio-description's narrator (\texttt{geo, groom > all non-geo}).
        Red: the primary $t$-contrast for the movie comparing cuts to a new
        setting with cuts to a familiar perspective (\texttt{vse\_new >
        vpe\_old}).
        Black: outline of overlapping individual PPA ROIs.
        \citep{sengupta2016extension}.}
    \label{fig:group-slices}
\end{figure*}

\subsection{individual results}
% why individual results in the first place.
We also investigated localization performance of both naturalistic paradigms on
the level of individual subjects. \todo{maybe report reason here, too: which
subjects influence the group results the most? ``multiple localizer''?}
% results in both subject and group space
Time series of all subjects were analyzed both in subject space and group space.
% why
Analysis in group space (Z>3.4, p<.05 cluster-corrected) was performed for
better comparison of results across participants.
% ref to figure
Figure \ref{fig:subs-thresh-ppa} depicts thresholded z-maps of the primary AO
and AV $t$-contrast and the outline of the individual PPAs
\citep{sengupta2016extension} overlayed on the MNI152 template (horizontal slice
z=-11 for all subjects).

% results in detail voxels of significant clusters in PPA ROI (and  RSC
% liberally)
% sub-01: PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (-/-)
% sub-02: PPA (l/r), AO (-/-), AV (-/r); RSC: AO (-/-), AV (-/-)
% sub-03: PPA (l/r), AO (-/-), AV (-/r); RSC: AO (-/-), AV (-/-)
% sub-04: PPA (-/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (-/-) !
% sub-05: PPA (l/r), AO (-/-), AV (-/-); RSC: AO (-/-), AV (-/-)
% sub-06: PPA (l/r), AO (l/r), AV (-/-); RSC: AO (l/-), AV (-/-)
% sub-09: PPA (l/r), AO (l/-), AV (l/r); RSC: AO (l/r), AV (l/r)
% sub-14: PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (-/-)
% sub-15: PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (l/r)
% sub-16: PPA (l/r), AO (l/r), AV (l/r); RSC: AO (l/r), AV (l/-)
% sub-17: PPA (l/r), AO (l/r), AV (l/r); RSC: AO (l/r), AV (l/r)
% sub-18: PPA (l/r), AO (l/r), AV (l/r); RSC: AO (l/r), AV (-/r)
% sub-19: PPA (l/r), AO (l/r), AV (-/r); RSC: AO (l/r), AV (l/r)
% sub-20: PPA (-/r), AO (-/-), AV (l/r); RSC: AO (-/-), AV (-/-)

% PPA ROI (Sengupta et al., 2016)
The dedicated localizer shows bilateral clusters in 12 subjects and unilateral
right clusters in two subjects (sub-04, sub-20).

% AO
AO stimulus shows bilateral clusters in nine subjects, and one significant cluster in the
left hemisphere in sub-09.
% subj-04
In sub-04, two homologous clusters are apparent, where the dedicated localizer
yielded only one cluster in the right hemisphere.

% AV
AV shows homologous clusters in five subjects, and unilateral right clusters in
seven subjects (of which one subjects also yielded just a unilateral cluster in
the dedicated localizer).
% difference to dedicated localizer
In sub-20 bilateral, where the dedicated localizer yielded only one cluster in
the right hemisphere

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/subs-thresh-ppa}
    \caption{Fixed-effects individual-level GLM results (Z>3.4, p<.05
        cluster-corrected). The brains of the 14 subjects are aligned via
        non-linear transformation to a study-specific T2* group template that is
    co-registered to the MNI152 template with an affine transformation (12
degrees of freedom) to facilitate comparisons across subjects.
        Light grey: The audio-description's field-of-view
        (cf. \citep{hanke2014audiomovie}).
        Blue: the primary $t$-contrast for the audio-description comparing
        geometry-related nouns to non geometry-related nouns spoken by the
        audio-description's narrator (\texttt{geo, groom > all non-geo}).
        Red: the primary $t$-contrast for the movie comparing cuts to a new
        setting with cuts to a familiar perspective (\texttt{vse\_new >
        vpe\_old}).
        Black: outline of subject-specific PPA ROI.}
\label{fig:subs-thresh-ppa}
\end{figure*}

\subsection{Bland-Altman-Plots}
% why
To better depict the agreement (and difference) between brain responses to the
visual localizer and contrast 1 of the AO paradigm, we created
Bland-Altman-Plots (see Figure \ref{fig:bland-altman}).
% what do Bland-Altman-Plots show?
The plots for the 14 subjects show the mean of z-values of two spatially
corresponding voxels in unthresholded z-maps on the x-axis and their difference
on the y-axis (dedicated localizer minus AO stimulus).
% masking
We constrained the number of voxels to voxels in the occipital and temporal
lobes (grey) using the (probabilistic) Jülich Histological Atlas
\citep{eickhoff2005toolbox, eickhoff2007assignment} to voxels located in the
PPA overlap of all subjects (blue), and voxels in the individual PPA
ROI(s)(red).

% what we can see
A shift of the distribution to voxels with a mean above zero can be seen the
further we constrain voxels to the individual PPA (KDE plot for the x-axis).
% but
Values above the horizontal line depict voxels that show a higher z-value in the
dedicated localizer, values below the horizontal line depict voxels that show
higher z-values in the AO stimulus.

\todo[inline]{the plots are ``biased'' in the PPA mask in such a way that they
don't take into account that clusters are not 100 perc. congruent, meaning the
AO stimulus has voxels in regions that are outside of the individual PPA ->
probably bias to show higher values for the dedicated localizer (red voxels)}

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/subjs_bland-altman.png}
    \caption{Bland-Altman-Plots for individual subjects. The x-axis depicts the
        mean of two spatially corresponding voxels in the unthresholded z-map of
        the visual localizer and in the unthresholded z-map of contrast 1 of the
        AO stimulus (KDE plot on the top). The y-axis depicts the difference of
        two voxels (KDE plot on the right). The overlays depict voxels spatially
        contrained to be located in the temporal and occipital cortex (grey),
    PPA overlap of all subjects (blue), and individual PPA (red).}
    \label{fig:bland-altman} \end{figure*}
